---
title: "Wine Ratings"
output: html_document
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(gridExtra) # plot grid handling

```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}
tt <- tt_load("2019-05-28")
wine_ratings <- tt$`winemag-data-130k-v2` %>% as.data.frame()
```


# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}


winery_list <- wine_ratings %>% 
  group_by(winery) %>%
  count() %>%
  arrange(desc(n))
  #17k wineries

wine_ratings %>% group_by(title) %>% count() %>% arrange(desc(n))

tasters <- wine_ratings %>%
  group_by(taster_name) %>%
  count() %>%
  arrange(desc(n))
    #same ~20 tasters for 80% of the ratings, 20% unknown / NA

varieties <- wine_ratings %>%
  group_by(variety) %>%
  count() %>%
  arrange(desc(n)) %>%
  as.data.frame()
    #700+ varieties!!! Note the wines in your cupboard are not listed :|


winery_list %>% 
  ggplot(aes(x=n)) + 
  geom_histogram() + 
  labs(title = "Histogram - distribution of wineries included",
       x = "number of wines",
       y = "")


library(tidytext)




```

``` {r}
library(tidylo)

# common words for raters
wine_stopwords <- c("wine")

winery_words <- wine_ratings %>% 
  unnest_tokens(word, description) %>%
  anti_join(stop_words) %>%
  filter(!word %in% wine_stopwords)
winery_words$word <- str_replace_all(winery_words$word, 
                                     "[[:digit:]]", "")


winery_wordcounts <- winery_words %>%
  group_by(word) %>%
  count() %>%
  arrange(desc(n))

rater_logodds <- winery_words %>%
  count(taster_name, word) %>%
  bind_log_odds(taster_name, word, n) %>%
  arrange(desc(log_odds_weighted))

plot_rater_common_words <- rater_logodds %>%
      group_by(taster_name) %>%
      slice_max(log_odds_weighted, n=10) %>%
      mutate(word = reorder_within(word, log_odds_weighted, taster_name)) %>%
      ggplot(aes(log_odds_weighted, word)) + 
      geom_col() + 
      facet_wrap(~taster_name, scales = "free_y") + 
      scale_y_reordered() + 
      labs(title = "Words commonly used by each rater, in description",
           x = "log odds (weighted) of description words by taster",
           y = "")

#todo - filter out tasters with < maybe 200 total reviews?
```

```{r}

# do the raters have favorite types of wine? 
commmon_varieties <- varieties %>%
  filter(n > 100) %>%
  select(variety)

rater_logodds_variety <- wine_ratings %>%
  count(taster_name, variety) %>%
  bind_log_odds(taster_name, variety, n) %>%
  arrange(desc(log_odds_weighted)) %>%
  filter(variety %in% commmon_varieties$variety)



plot_rater_common_varieties <- rater_logodds_variety %>%
      group_by(taster_name) %>%
      slice_max(log_odds_weighted, n=10) %>%
      mutate(variety = reorder_within(variety, log_odds_weighted, taster_name)) %>%
      ggplot(aes(log_odds_weighted, variety)) + 
      geom_col() + 
      facet_wrap(~taster_name, scales = "free_y") + 
      scale_y_reordered() + 
      labs(title = "Varieties commonly reviewed by each rater",
           x = "log odds (weighted) of wine variety for each taster",
           y = "")
```

```{r}
# What words go with most common wines?

commmon_varieties <- varieties %>% 
  as.data.frame() %>%
  filter(!is.na(variety)) %>%
  slice_max(n, n=12)
  
variety_words <- varieties %>% 
  as.data.frame() %>%
  unnest_tokens(word, variety) %>%
  filter(!is.na(word))

more_variety_words <- c("cab", "zin", "cabs", "pinots","sb",
                        "rieslings", "chardonnays", "blancs", 
                        "sample", "cru", "cabernets", "chard",
                        "chianti","noirs","syrahs")

winery_words <- wine_ratings %>% 
  unnest_tokens(word, description) %>%
  anti_join(stop_words) %>%
  filter(!word %in% wine_stopwords)

variety_words_logodds <- winery_words %>%
  count(variety, word) %>%
  bind_log_odds(variety, word, n) %>%
  arrange(desc(log_odds_weighted)) %>%
  filter(variety %in% commmon_varieties$variety,
         !word %in% variety_words$word, 
         !word %in% more_variety_words)


plot_variety_common_words <- variety_words_logodds %>%
      group_by(variety) %>%
      slice_max(log_odds_weighted, n=10) %>%
      mutate(word = reorder_within(word, log_odds_weighted, variety)) %>%
      ggplot(aes(log_odds_weighted, word)) + 
      geom_col(aes(fill = variety)) + 
      facet_wrap(~variety, scales = "free_y", ncol = 3) + 
      scale_y_reordered() + 
      labs(title = "Wine descriptive words most specific to different varieties",
           x = "log odds (weighted) of word in each variety",
           y = "")

plot_variety_common_words + theme_bw() + 
      theme(legend.position = "none")

```

```{r}
# What words are used to describe expensive vs cheap wines, or low points to high points? 
```


```{r}
# Do people say more or less about good wines?

descrip_chars_vs_points <- wine_ratings %>%
  mutate(descrip_char = nchar(description),
         descrip_words = str_count(description, '\\w+')) %>%
  ggplot(aes(x=descrip_char, y = points)) + 
  geom_point() + 
  labs(title = "wine description length vs point score",
       x = "description length (# characters)",
       y = "points") + 
  geom_smooth(method = "lm", se = F) + theme_bw()

descrip_words_vs_points <- wine_ratings %>%
  mutate(descrip_char = nchar(description),
         descrip_words = str_count(description, '\\w+')) %>%
  ggplot(aes(x=descrip_words, y = points)) + 
  geom_point() + 
  labs(title = "wine description length vs point score",
       x = "description length (# words)",
       y = "points") + 
  geom_smooth(method = "lm", se = F) + theme_bw()

# are the words themselves longer? No not really

descrip_word_length_vs_points <- winery_words %>%
  group_by(...1, points, variety) %>%
  summarize(avg_word_length = mean(nchar(word))) %>%
  ggplot(aes(x=avg_word_length, y = points)) + 
  geom_point() + 
  labs(title = "wine description word length vs point score",
       x = "average description word length (characters)",
       y = "points") + 
  geom_smooth(method = "lm", se = F) + theme_bw()


grid.arrange(descrip_chars_vs_points, descrip_words_vs_points, descrip_word_length_vs_points, ncol = 3)

# what about the words people use for expensive / cheap wine? 
winery_words #from earlier -- turn to words, remove stop_words and wine_stopwords, remove digits)

# set up dummy vars for TOP wines -- points or price? 
low_cutoff_score <- 85
mid_cutoff_score <- 95
low_cutoff_price <- 20
mid_cutoff_price <- 1000
generic_stopwords <- c("flavors")


winery_words <- winery_words %>%
  filter(!word %in% generic_stopwords) %>%
  mutate(price_var = case_when(price < low_cutoff_price ~ "Low", price >= low_cutoff_price & price < mid_cutoff_price ~"Mid", TRUE ~ "High"),
         score_var = case_when(points < low_cutoff_score ~ "Low", points >= low_cutoff_score & points < mid_cutoff_score ~"Mid", TRUE ~ "High"))

price_logodds <- winery_words %>%
  filter(word != "") %>%
  count(price_var, word) %>%
  bind_log_odds(price_var, word, n) %>%
  arrange(desc(log_odds_weighted))

price_logodds$price_var <- as.factor(price_logodds$price_var)

plot_price_common_words <- price_logodds %>%
      group_by(price_var) %>%
      slice_max(log_odds_weighted, n=10) %>%
      mutate(word = reorder_within(word, log_odds_weighted, price_var)) %>%
      mutate(price_var = factor(price_var, levels=c("Low","Mid","High"))) %>%
      ggplot(aes(log_odds_weighted, word, fill = price_var)) + 
      geom_col() + 
      facet_wrap(~ price_var, scales = "free_y") + 
      scale_y_reordered() + 
      labs(title = "Wine description words commonly used by each price range",
           subtitle = "Low: up to $50, Mid; 50-$1000, High: >$1000",
           x = "log odds (weighted) of description words by price range",
           y = "") + 
      theme_bw() + 
      theme(legend.position = "none")

rating_logodds <- winery_words %>%
  filter(word != "") %>%
  count(score_var, word) %>%
  bind_log_odds(score_var, word, n) %>%
  arrange(desc(log_odds_weighted))

rating_logodds$score_var <- as.factor(rating_logodds$score_var)

plot_rating_common_words <- rating_logodds %>%
      group_by(score_var) %>%
      slice_max(log_odds_weighted, n=10) %>%
      mutate(word = reorder_within(word, log_odds_weighted, score_var)) %>%
      mutate(score_var = factor(score_var, levels=c("Low","Mid","High"))) %>%
      ggplot(aes(log_odds_weighted, word, fill = score_var)) + 
      geom_col() + 
      facet_wrap(~ score_var, scales = "free_y") + 
      scale_y_reordered() + 
      labs(title = "Wine description words commonly used by each ratings range (80-100)",
           subtitle = "Low: up to 85 points, Mid; 85-95, High: >95",
           x = "log odds (weighted) of description words by rating category",
           y = "") + 
      theme_bw() + 
      theme(legend.position = "none")


grid.arrange(plot_price_common_words, plot_rating_common_words, ncol = 2)

```

```{r}
# look at rating, price, and country relationships

# boxplot - ratings
boxplot_wine_points <- wine_ratings %>%
  filter(!is.na(country)) %>%
  filter(price <= 50) %>%
  ggplot(aes(x=points, y = reorder(country, points))) + 
  geom_boxplot(outlier.size=0.1) +
  theme_bw() + 
  labs(title = "Wine ratings", 
       x = "points (80-100)",
       y = "")

# boxplot - Price
boxplot_wine_price <- wine_ratings %>%
  filter(!is.na(country)) %>%
  filter(price <= 50) %>%
  ggplot(aes(x=price, y = reorder(country, price))) + 
  geom_boxplot(outlier.size=0.1) +
  theme_bw() + 
  labs(title = "Wine price for each country",
       x = "price (USD)",
       y = "")

# Look at ratio of points / price
country_price_point_ratio <- wine_ratings %>%
  filter(!is.na(country),
         !is.na(price)) %>%
  filter(price <= 50) %>%
  group_by(country) %>%
  mutate(price_rating_ratio = (points / price),
         avg_country_price = ave(price, country),
         median_country_price = median(price)) %>%
  ggplot(aes(x = price_rating_ratio, y = reorder(country, price_rating_ratio), color = avg_country_price)) + 
  geom_boxplot(outlier.size=0.1) + 
  theme_bw() + 
  scale_color_gradient(low = "blue", high = "red") +
  labs(title = "Wine ratings ratio",
       x = " points / dollar",
       y = "",
       color = "Median\nwine\nprice\n(USD)") #+ 


grid.arrange(boxplot_wine_points, boxplot_wine_price, country_price_point_ratio, ncol = 3)

```

```{r}
# price vs rating for different wine types



#facet by variety - narrow down to common 
commmon_varieties <- varieties %>% 
  as.data.frame() %>%
  filter(!is.na(variety)) %>%
  slice_max(n, n=12)

log_wine_ratings_price <- wine_ratings %>% 
  filter(variety %in% commmon_varieties$variety) %>% 
         #price < 1000) %>%
  mutate(log_price = log(price))

log_wine_ratings_price %>%
  ggplot(aes(x=points, y = log_price, color = variety)) + 
  facet_wrap(~variety, ncol = 6) + 
  geom_point(size = 0.2) + 
  labs(title = "wine log(price) vs point score",
       x = "Rating",
       y = "log(Price)") + 
  geom_smooth(method = "lm", se = F) +
  theme_bw() + 
  theme(legend.position = "none")

# regression lines appear a little different, let's check!
library(lsmeans)

#log_wine_ratings_price$variety <- as.factor(log_wine_ratings_price$variety)

# fit the linear model
logprice_model <- aov(log_price ~ points + variety, data = log_wine_ratings_price)
summary(logprice_model)
  # points, variety, and their interaction are all significant contributors to price

# look at coeffs, 
logprice_model$coefficients

# how to interpret: 
# with price not changing, a cab sauv bottle will be exp(0.11066156) = 1.1170167 or ~12% more expensive than a bordeaux-style red blend
exp(logprice_model$coefficients)

#pairwise comparisons
TukeyHSD(logprice_model, "variety")

pairwise.t.test(log_wine_ratings_price$log_price, log_wine_ratings_price$variety, p.adjust.method = "bonferroni")

#slopes
lm_price_points_variety$coefficients
list_test <- lstrends(lm_price_points_variety, "variety", var="points")

#compare slopes
pairs(list_test) #(LOTS of comparisons, bonferroni correction so use alpha .05/66 or 0.0008 for sig)
  # looks like coefficients that ARE roughly similar are Nebbiolo, Rose, Sauv Blanc, and Syrah; also Red Blend, Reisling, and Cab . Bordeaux style red blend and Cab Sauv are also not different. 
```

```{r}
# predict score based on price, province, region 1 / 2, winery


```

