---
title: "Wine Ratings"
output: html_document
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)

```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}
tt <- tt_load("2019-05-28")
wine_ratings <- tt$`winemag-data-130k-v2` %>% as.data.frame()
```


# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}


winery_list <- wine_ratings %>% 
  group_by(winery) %>%
  count() %>%
  arrange(desc(n))
  #17k wineries

wine_ratings %>% group_by(title) %>% count() %>% arrange(desc(n))

tasters <- wine_ratings %>%
  group_by(taster_name) %>%
  count() %>%
  arrange(desc(n))
    #same ~20 tasters for 80% of the ratings, 20% unknown / NA

varieties <- wine_ratings %>%
  group_by(variety) %>%
  count() %>%
  arrange(desc(n)) %>%
  as.data.frame()
    #700+ varieties!!! Note the wines in your cupboard are not listed :|


winery_list %>% 
  ggplot(aes(x=n)) + 
  geom_histogram() + 
  labs(title = "Histogram - distribution of wineries included",
       x = "number of wines",
       y = "")

wine_ratings %>% 
  ggplot(aes(x=points, y = price, fill = variety)) + 
  geom_point() + 
  labs(title = "wine price vs point score",
       x = "Rating",
       y = "Price")
library(tidytext)




```

``` {r}
library(tidylo)

# common words for raters
wine_stopwords <- c("wine")

winery_words <- wine_ratings %>% 
  unnest_tokens(word, description) %>%
  anti_join(stop_words) %>%
  filter(!word %in% wine_stopwords)
winery_words$word <- str_replace_all(winery_words$word, 
                                     "[[:digit:]]", "")


winery_wordcounts <- winery_words %>%
  group_by(word) %>%
  count() %>%
  arrange(desc(n))

rater_logodds <- winery_words %>%
  count(taster_name, word) %>%
  bind_log_odds(taster_name, word, n) %>%
  arrange(desc(log_odds_weighted))

plot_rater_common_words <- rater_logodds %>%
      group_by(taster_name) %>%
      slice_max(log_odds_weighted, n=10) %>%
      mutate(word = reorder_within(word, log_odds_weighted, taster_name)) %>%
      ggplot(aes(log_odds_weighted, word)) + 
      geom_col() + 
      facet_wrap(~taster_name, scales = "free_y") + 
      scale_y_reordered() + 
      labs(title = "Words commonly used by each rater, in description",
           x = "log odds (weighted) of description words by taster",
           y = "")

#todo - filter out tasters with < maybe 200 total reviews?
```

```{r}

# do the raters have favorite types of wine? 
commmon_varieties <- varieties %>%
  filter(n > 100) %>%
  select(variety)

rater_logodds_variety <- wine_ratings %>%
  count(taster_name, variety) %>%
  bind_log_odds(taster_name, variety, n) %>%
  arrange(desc(log_odds_weighted)) %>%
  filter(variety %in% commmon_varieties$variety)



plot_rater_common_varieties <- rater_logodds_variety %>%
      group_by(taster_name) %>%
      slice_max(log_odds_weighted, n=10) %>%
      mutate(variety = reorder_within(variety, log_odds_weighted, taster_name)) %>%
      ggplot(aes(log_odds_weighted, variety)) + 
      geom_col() + 
      facet_wrap(~taster_name, scales = "free_y") + 
      scale_y_reordered() + 
      labs(title = "Varieties commonly reviewed by each rater",
           x = "log odds (weighted) of wine variety for each taster",
           y = "")
```

```{r}
# What words go with most common wines?

commmon_varieties <- varieties %>% 
  as.data.frame() %>%
  filter(!is.na(variety)) %>%
  slice_max(n, n=12)
  
variety_words <- varieties %>% 
  as.data.frame() %>%
  unnest_tokens(word, variety) %>%
  filter(!is.na(word))

more_variety_words <- c("cab", "zin", "cabs", "pinots","sb",
                        "rieslings", "chardonnays", "blancs", 
                        "sample", "cru")

winery_words <- wine_ratings %>% 
  unnest_tokens(word, description) %>%
  anti_join(stop_words) %>%
  filter(!word %in% wine_stopwords)

variety_words_logodds <- winery_words %>%
  count(variety, word) %>%
  bind_log_odds(variety, word, n) %>%
  arrange(desc(log_odds_weighted)) %>%
  filter(variety %in% commmon_varieties$variety,
         !word %in% variety_words$word, 
         !word %in% more_variety_words)


plot_variety_common_words <- variety_words_logodds %>%
      group_by(variety) %>%
      slice_max(log_odds_weighted, n=10) %>%
      mutate(word = reorder_within(word, log_odds_weighted, variety)) %>%
      ggplot(aes(log_odds_weighted, word)) + 
      geom_col(aes(fill = variety)) + 
      facet_wrap(~variety, scales = "free_y", ncol = 3) + 
      scale_y_reordered() + 
      labs(title = "Wine descriptive words most specific to different varieties",
           x = "log odds (weighted) of word in each variety",
           y = "")

plot_variety_common_words + theme_bw() + 
      theme(legend.position = "none")

```

```{r}
# look at vintage and points by region, to find the best sources / years
```

```{r}
# price vs rating for different wine types
```

```{r}
# predict score based on price, province, region 1 / 2, winery

```

